New blog under construction

### 2022-01-28 _posts/welcome/welcome.Rmd
update welcome and rebuild

This is a re-launch of slinberg.net, using the [Distill](https://rstudio.github.io/distill) platform to align with the UMASS DACSS program I am presently enrolled in.

>>>>

This is a re-launch of slinberg.net, using the [distill](https://rstudio.github.io/distill) platform to align with the [UMASS DACSS program](https://www.umass.edu/sbs/data-analytics-and-computational-social-science-program/ms) I am presently enrolled in.

Pardon the dust while we redecorate. First up will be a soup-to-nuts, zero-to-hero walkthrough of how this site was built and deployed.
